HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-10 scnn.tex
related work: relational reasoning

Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign},
segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, etc.
By adding a recurrent neural network on top \citep{seo2016gcrn}, they can for example model time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
% scientifically and industrially motivated applications

>>>>

Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign}, segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, and many more.
By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
% scientifically and industrially motivated applications
